Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-12 Presentation/slides.tex
Edit simulation in main.tex, edit presentation

		\begin{itemize}
			\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
			\item Only observed at $x_{i}(t_{j,i})$
			\item Growth curves, financial data, human perception (pitch), ...
			\item To abstract information from the curves, they must be interpretable!
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Simulation Setup \& Application}
		\begin{itemize}
			\item Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
			\item Generate \textbf{similar curves} from gasoline dataset:
		\end{itemize}

		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

	\begin{frame}{Simulation Setup \& Application cont.}

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		Let 
		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$

		where $Z \sim \mathcal{N}(0,1)$ be two responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{itemize}
    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (5,6,...,25)$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP,...)
			\item {\color{green} add results here!}
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation Setup \& Application cont.}
		\begin{itemize}
		\item
    		Use insights from the simulation study to uncover dependence.
    		\item
    		Similar setup, but using only bsplie basis expansion and initial 60 spectral curves.
    		\item
    		Validation set approach:	Scores of testdata needs to be estimated by the trainingdata.  {\color{green} explain in detail?}
    		\item
    		Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}

	\begin{frame}{Summary}
		Jona \\
		Just summarize what we have done...
	\end{frame}

@@

	\begin{frame}{Further Reading}
		 Put footnotes here!
	\end{frame}

>>>>

		\begin{itemize}
			\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
			\item Only observed at $x_{i}(t_{j,i})$
			\item Example: Gasoline dataset (60 x 400)
			\item Other Examples: Growth curves, financial data, human perception (pitch), ...

		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Simulation Setup}
		\begin{itemize}
			\item Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
			\item Generate \textbf{similar curves} from gasoline dataset:
		\end{itemize}

		$$\tilde{X}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{X}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

@@

	\begin{frame}{Simulation Setup cont.}

@@

	\begin{frame}{Simulation Setup cont.}
		Let 
		$$Y_{1,f} = \langle NIR, f\rangle + Z\left(  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)\right)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z\left( \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)\right)$$

		where $Z \sim \mathcal{N}(0,1)$ be two responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{itemize}
    		\item Four combinations with different number of cubic basis-function $n_{basis} \in (4,5,...,25)$ and fourier functions $(1,3,...,25)$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP,...)

		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation Results}

		\begin{itemize}

			\item {\color{green} add results here!}
		\end{itemize}
	\end{frame}

	\begin{frame}{Application setup}
		\begin{itemize}
		\item
    		Use insights from the simulation study to uncover dependence.
    		\item
    		Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
    		\item
    		Validation set approach:	Scores of test data needs to be estimated by the training data. 
    		\item
    		Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}

	\begin{frame}{Summary}
		\begin{itemize}
		\item
    		Concepts of functional data: 
    		\begin{itemize}
			\item See dataset as smooth curve than as set of discrete measurements.
    			\item Theory of Random Functions, motivated from random variable.
    			\item Basis expansion and its Bias-Variance tradeoff.
    			\item Scalar on Function Regression via Basis Expansion.
    			\item Functional principal component Analysis and FPCR.
		\end{itemize}
    		\item
    		Simulation study results: specification depends on function and signal-to-noise ratio
    		\item
    		% Guided you  from the beginning to the end of the presentaion through one application ....
    		Guided through application to predict octane ratings.

		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Further Reading}
		 Put footnotes here!
		 Yuanpeng Li et al.(2020): Early Diagnosis of Type 2 Diabetes Based on Near-Infrared Spectroscopy Combined With Machine Learning and Aquaphotomics, Frontiers of Chemistry (8)
	\end{frame}
